---
title             : "Study 2"
shorttitle        : "Moral Dilution"
author:
  - name          : "Blinded"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Blinded"
    email         : "Blinded"
  - name          : "Blinded"
    affiliation   : "2"
  - name          : "Blinded"
    affiliation   : "1"
  - name          : "Blinded"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "Blinded"
  - id            : "2"
    institution   : "Blinded"
author_note: >
  All procedures performed in studies involving human participants were approved by institutional research ethics committee and conducted in accordance with the Code of Professional Ethics of the Psychological Society of Ireland, and with the 1964 Helsinki declaration and its later amendments or comparable ethical standards. Informed consent was obtained from all individual participants included in the study. The authors declare that there are no potential conflicts of interest with respect to the research, authorship, and/or publication of this article. All authors consented to the submission of this manuscript.
abstract: >
  Six studies etc.
keywords          : "keywords"
wordcount         : "TBC"
bibliography: "../resources/bib/My Library.bib"
csl: "../resources/bib/apa6.csl"
figsintext        : true
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
toc               : false
lang              : "en-US"
documentclass     : "apa7"
output:
  papaja::apa6_pdf
header-includes:
- \raggedbottom
editor_options: 
  chunk_output_type: console
---


```{r S4setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE)
# knitr::opts_chunk$set(eval = TRUE, echo = TRUE)
#knitr::opts_chunk$set(include = FALSE)
```


```{r S4load_libraries_cogload}
rm(list = ls())
library(citr)
#install.packages("sjstats")
library(plyr)
library(foreign)
library(car)
library(desnum)
library(ggplot2)
library(extrafont)
#devtools::install_github("crsh/papaja")
library(papaja)
#library("dplyr")
library("afex")
library("tibble")
library(scales)
#install.packages("metap")
library(metap)
library(pwr)
library(lsr)
#install.packages("sjstats")
library(sjstats)
library(DescTools)
#inatall.packages("ggstatsplot")
#library(ggstatsplot)
library(VGAM)
library(nnet)
library(mlogit)
library(reshape2)
#install.packages("powerMediation")
library("powerMediation")
library("ggpubr")


# library(rstatix)


#source("load_all_data.R")

#devtools::install_github("benmarwick/wordcountaddin")
#library(wordcountaddin)
#wordcountaddin::text_stats("cogload_1to5_25Sept19.Rmd")
#setwd("manuscript_prep")
getwd()
```



```{r S4LoadData}
#source("~/Dropbox/College/research/Research_general/cog_load/moral_dumbfounding_and_cognitive_load/read_and_sort_raw_data.R")
#source("~/Dropbox/College/research/Research_general/cog_load/moral_dumbfounding_and_cognitive_load/load_study6_data.R")
rm(list = ls())

df3 <- read.csv("../data/study4_rep_data_long.csv")
df1 <- read.csv("../data/study4_rep_data_wide.csv")
x <- read.csv("../data/study4_rep_data_long_clean.csv")

MPS <- x %>% 
  select(R1,R2,R3,R4)

alpha1 <- ltm::cronbach.alpha(MPS)

alpha1
```

# Study 4 - Good Characters
Following the divergent results for morally good characters between Studies 2 and 3, Study 4 was an attempted replication of Study 2.

## Study 4: Method

### Study 4: Participants and design
The design, materials, and procedure for Study 4 were the same as for Study 2, the only change from Study 2 was that all participants in Study 4 were recruited from MTurk. Study 4 was a within-subjects design. The independent variable was condition with two levels, diagnostic and non-diagnostic. We used the same two dependent variables as in previous studies, the four item moral perception scale (MPS-4, $\alpha$ = `r round(alpha1$alpha,digits=2)`), and the single item moral perception measure MM-1.

A total sample of `r length(levels(as.factor(df3$ResponseId)))` (`r sum(df1$gender=="1",na.rm=T)` female, `r sum(df1$gender=="2", na.rm=T)` male, `r round(sum(df1$gender=="3", na.rm=T)/1)` non-binary, `r round(sum(df1$gender=="4", na.rm=T))` other; `r sum(df1$gender=="5", na.rm=T)` prefer not to say, *M*~age~ = `r round(mean(df3$age, na.rm=T),digits=2)`, min = `r min(df3$age, na.rm=T)`, max = `r max(df3$age, na.rm=T)`, *SD* = `r round(sd(df3$age, na.rm=T),digits=2)`) started the survey.  Participants were recruited from MTurk and paid $0.40 for their participation.

```{r}
df1 <- read.csv("../data/study4_rep_data_long.csv")
df3 <- read.csv("../data/study4_rep_data_long_clean.csv")
df_long_clean <- df3
table(df3$gender)
length(df1$gender)/6
length(levels(as.factor(df1$ResponseId)))-length(levels(as.factor(df3$ResponseId)))
length(df3$gender)/4

att_both <- length(levels(as.factor(df1$ResponseId)))-length(levels(as.factor(df3$ResponseId)))
```

Participants who failed both manipulation checks were removed (*n* = `r att_both`), leaving a total sample of `r length(df3$gender)/4` participants (`r sum(df3$gender=="1",na.rm=T)/4` female, `r sum(df3$gender=="2", na.rm=T)/4` male, `r sum(df3$gender=="4", na.rm=T)/4` other, `r sum(df3$gender=="4", na.rm=T)/4` prefer not to say; *M*~age~ = `r round(mean(df3$age, na.rm=T),digits=2)`, min = `r min(df3$age, na.rm=T)`, max = `r max(df3$age, na.rm=T)`, *SD* = `r round(sd(df3$age, na.rm=T),digits=2)`).

### Study 4: Procedure and materials
All materials and procedures were the same as in Study 2.

## Study 4: Results

```{r}
x <- df3
sam <- x[which(x$scenario=="sam"),]
francis <- x[which(x$scenario=="francis"),]
alex <- x[which(x$scenario=="alex"),]
robin <- x[which(x$scenario=="robin"),]

```

```{r}
x <- df3
# bad <- x[which(x$condition=="diagnostic"),]
# good <- x[which(x$condition=="non-diagnostic"),]
#good$scenario_abb <- droplevels(good$scenario_abb)

#x <- bad
aov_full <- rstatix::anova_test(
  data=x
  , dv=R_tot
  , wid = ResponseId
  , within = scenario)
aov1 <- rstatix::get_anova_table(aov_full)
aov1
aov1$DFd

pwc <- x %>%
  rstatix::pairwise_t_test(
    R_tot ~ scenario, paired = TRUE,
    p.adjust.method = "bonferroni"
    )
pwc
p_report(pwc$p[2])

# d1 <- lsr::cohensD(R_tot~condition,x,method="paired")
# t.test(R_tot~condition,x,paired=TRUE)
# t1 <- t.test(x$R_tot~x$scenario,paired=TRUE)
# d1
lapply(pwc$p.adj,p_report)
```




The means and standard deviations for MPS-4 for each scenario are as follows: 
*Sam*,
*M*~MPS-4~ = `r mean(sam$R_tot)`, *SD*~MPS-4~ = `r sd(sam$R_tot)`,
*Francis*,
*M*~MPS-4~ = `r mean(francis$R_tot)`, *SD*~MPS-4~ = `r sd(francis$R_tot)`,
*Alex*,
*M*~MPS-4~ = `r mean(alex$R_tot)`, *SD*~MPS-4~ = `r sd(alex$R_tot)`,
*Robin*,
*M*~MPS-4~ = `r mean(robin$R_tot)`, *SD*~MPS-4~ = `r sd(robin$R_tot)`. There was significant variation depending on the description, *F*(`r round(aov1$DFn)`,`r round(aov1$DFd)`) = `r aov1$F`, *p* `r paste(p_report(aov1$p))`, partial $\eta$^2^ = `r aov1$ges`. Pairwise comparisons did not reveal any significant differences between individual descriptions (all *p*s > .05).



```{r}
x <- df3
# bad <- x[which(x$condition=="diagnostic"),]
# good <- x[which(x$condition=="non-diagnostic"),]
#good$scenario_abb <- droplevels(good$scenario_abb)

#x <- bad
aov_full <- rstatix::anova_test(
  data=x
  , dv=M1
  , wid = ResponseId
  , within = scenario)
aov1 <- rstatix::get_anova_table(aov_full)
aov1
aov1$DFd

pwc <- x %>%
  rstatix::pairwise_t_test(
    M1 ~ scenario, paired = TRUE,
    p.adjust.method = "bonferroni"
    )
pwc
p_report(pwc$p[2])
lapply(pwc$p.adj, p_report)
paste(pwc$p.adj[2])
pwc$p[2]
# d1 <- lsr::cohensD(M1~condition,x,method="paired")
# t.test(M1~scenario,x,paired=TRUE)
# t1 <- t.test(x$M1~x$scenaro,paired=TRUE)
# d1

```

The means and standard deviations for MM-1 for each scenario are as follows: 
*Sam* (diagnostic/moral),
*M*~MM-1~ = `r mean(sam$M1)`, *SD*~MM-1~ = `r sd(sam$M1)`;
*Francis* (diagnostic/moral),
*M*~MM-1~ = `r mean(francis$M1)`, *SD*~MM-1~ = `r sd(francis$M1)`;
*Alex* (diagnostic/moral),
*M*~MM-1~ = `r mean(alex$M1)`, *SD*~MM-1~ = `r sd(alex$M1)`;
*Robin* (diagnostic/moral),
*M*~MM-1~ = `r mean(robin$M1)`, *SD*~MM-1~ = `r sd(robin$M1)`. There was significant variation depending on the description, *F*(`r round(aov1$DFn)`,`r round(aov1$DFd)`) = `r aov1$F`, *p* `r paste(p_report(aov1$p))`, partial $\eta$^2^ = `r paste(aov1$ges)`. Pairwise comparisons did not reveal any significant differences between individual descriptions (all *p*s > .05).



```{r}
x <- df3
model0 <- lmerTest::lmer(R_tot ~ 1
                #   condition
                 + (1|ResponseId)
                # + (1|ResponseId:condition)
                , data = x
          #      , contrasts = list(condition = contr.sum  , valence = contr.sum)
            )

summary(model0)
model1 <- lmerTest::lmer(R_tot ~
                  condition*scenario
                + (1|ResponseId)
                + (1|ResponseId:condition)
                , data = x
                , contrasts = list(condition = contr.sum  , scenario = contr.sum)
            )
summary(model1)
anova(model1)
results_anova <- as.data.frame(anova(model0,model1))
results_anova
results_anova$Chisq[2]
results_anova$Df
p1 <- results_anova$`Pr(>Chisq)`[2]
p_report(p1)
#p_report(results_anova$`Pr(>Chisq)`)[2]
results_anova$AIC
summary_model1 <- summary(model1)
summary_model1
results_coef <- as.data.frame(summary_model1$coefficients)

aov1 <- anova(model1)
f3 <- aov1$`F value`[1]
p3 <- aov1$`Pr(>F)`[1]

results_coef$Estimate[2]
results_coef$`Std. Error`[2]
results_coef$df[2]
t1 <- results_coef$`t value`[2]
p2 <- results_coef$`Pr(>|t|)`[2]

#QuantPsyc::lm.beta(results_coef)
anova(model1)
```

We conducted a linear-mixed-effects model to test if condition influenced MPS-4 responses. Our outcome measure was MPS-4, our predictor variable was condition; we allowed intercepts and the effect of condition to vary across participants, and scenario was also included in the model.
Overall, the model significantly predicted participants responses, and provided a better fit for the data than the baseline model, $\chi$^2^(`r results_anova$Df[2]`) = `r results_anova$Chisq[2]`, *p* `r paste(p_report(p1))`. Condition did not influence responses to the MPS-4, *F*(`r aov1$NumDF[1]`, `r aov1$DenDF[1]`) = `r f3`, *p* `r paste(p_report(p3))`; and was not a significant predictor in the model when controlling for scenario, $b$ = `r results_coef$Estimate[2]`, *t*(`r round(results_coef$df[2])`) = `r t1`, *p* `r paste(p_report(p2))`, see Figure\ \@ref(fig:S4bothconditionplot).

```{r S4Rtotconditionplot, fig.cap="Study 2: Differences in MPS-4 depending on condition", include=FALSE}

mps4plot <- 
ggplot(x,aes(x=condition,y=R_tot))+
  geom_violin() +
  stat_summary(fun=mean, geom="point", shape=23, size=2)+
  geom_boxplot(width=0.1)+
#  geom_dotplot(binaxis='y', stackdir='center', dotsize=.05)+
# violin plot with jittered points
# 0.2 : degree of jitter in x direction
  geom_jitter(shape=16
              , position=position_jitter(0.15)
              , size=.1
              , color="dark grey") +
  xlab("Condition") +
  ylab("Moral Perception Scale (MPS-4)") +
  theme_bw() +
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
        panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
                                size=12
                                ),
        legend.text=element_text(#family="Times",
                                 size=8
                                 ),
          legend.title=element_text(#family="Times",
                                    size=10
                                    ),
          axis.text=element_text(#family="Times",
                                 colour = "black",
                                 size=8
                                 ),
          axis.ticks.x = element_blank(),
          axis.title=element_text(#family="Times",
                                  size=12
                                  ),
          strip.text=element_text(#family = "Times",
                                  size = 12
                                  ),
         # strip.background = element_rect(fill = "white"),
          legend.position="right")




```


```{r S4M1conditionplot, fig.cap="Study 2: Differences in MM1 depending on condition", include=FALSE}

M1plot <- 
  ggplot(x,aes(x=condition,y=M1))+
  geom_violin() +
  stat_summary(fun=mean, geom="point", shape=23, size=2)+
  geom_boxplot(width=0.1)+
  #  geom_dotplot(binaxis='y', stackdir='center', dotsize=.05)+
  # violin plot with jittered points
  # 0.2 : degree of jitter in x direction
  geom_jitter(shape=16
              , position=position_jitter(0.15)
              , size=.1
              , color="dark grey") +
  xlab("Condition") +
  ylab("Moral Perception Measure (MM-1)")+
  theme_bw() +
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
        panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
          size=12
        ),
        legend.text=element_text(#family="Times",
          size=8
        ),
        legend.title=element_text(#family="Times",
          size=10
        ),
        axis.text=element_text(#family="Times",
          colour = "black",
          size=8
        ),
        axis.ticks.x = element_blank(),
        axis.title=element_text(#family="Times",
          size=12
        ),
        strip.text=element_text(#family = "Times",
          size = 12
        ),
        # strip.background = element_rect(fill = "white"),
        legend.position="right")




```

```{r}
figure <- ggarrange(mps4plot
                    , M1plot
                    #,labels = c("A")
                    , ncol = 2
                    , nrow = 1
                    , widths = c(0.485, 0.5))
figure
```


```{r S4bothconditionplot, fig.cap="Study 2: Differences in moral perception depending on condition", include=TRUE}

suppressWarnings(print(figure))

```



```{r}
model0 <- lmerTest::lmer(M1 ~ 1
                #   condition
                 + (1|ResponseId)
                # + (1|ResponseId:condition)
                , data = x
                #, contrasts = list(condition = contr.sum  , valence = contr.sum)
            )

summary(model0)
model1 <- lmerTest::lmer(M1 ~
                  condition*scenario
                + (1|ResponseId)
                + (1|ResponseId:condition)
                , data = x
                , contrasts = list(condition = contr.sum  , scenario = contr.sum)
            )
summary(model1)
anova(model1)
results_anova <- as.data.frame(anova(model0,model1))
results_anova
results_anova$Chisq[2]
results_anova$Df
p1 <- results_anova$`Pr(>Chisq)`[2]
p_report(p1)
#p_report(results_anova$`Pr(>Chisq)`)[2]
results_anova$AIC
summary_model1 <- summary(model1)


results_coef <- as.data.frame(summary_model1$coefficients)

aov1 <- anova(model1)
f3 <- aov1$`F value`[1]
p3 <- aov1$`Pr(>F)`[1]


results_coef$Estimate[2]
results_coef$`Std. Error`[2]
results_coef$df[2]
results_coef$`t value`[2]
t1 <- results_coef$`t value`[2]

p2 <- results_coef$`Pr(>|t|)`[2]

#QuantPsyc::lm.beta(results_coef)
anova(model1)
```


We conducted a linear-mixed-effects model to test if condition influenced MM-1 responses. Our outcome measure was MM-1, our predictor variable was condition; we allowed intercepts and the effect of condition to vary across participants. Overall, the model significantly predicted participants responses, and provided a better fit for the data than the baseline model, $\chi$^2^(`r results_anova$Df[2]`) = `r results_anova$Chisq[2]`, *p* `r paste(p_report(p1))`. Condition significantly influenced MM-1 responses *F*(`r round(aov1$NumDF[1])`, `r round(aov1$DenDF[1])`) = `r f3`, *p* `r paste(p_report(p3))`, and was a significant predictor in the model $b$ = `r results_coef$Estimate[2]`, *t*(`r round(results_coef$df[2])`) = `r t1`, *p* `r paste(p_report(p2))`, see Figure\ \@ref(fig:S4bothconditionplot).

In the supplementary analyses we report the effect of condition on moral perception for each description individually.




