---
title             : "Study 3"
shorttitle        : "Moral Dilution"
author:
  - name          : "Blinded"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Blinded"
    email         : "Blinded"
  - name          : "Blinded"
    affiliation   : "2"
  - name          : "Blinded"
    affiliation   : "1"
  - name          : "Blinded"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "Blinded"
  - id            : "2"
    institution   : "Blinded"
author_note: >
  All procedures performed in studies involving human participants were approved by institutional research ethics committee and conducted in accordance with the Code of Professional Ethics of the Psychological Society of Ireland, and with the 1964 Helsinki declaration and its later amendments or comparable ethical standards. Informed consent was obtained from all individual participants included in the study. The authors declare that there are no potential conflicts of interest with respect to the research, authorship, and/or publication of this article. All authors consented to the submission of this manuscript.
abstract: >
  Six studies etc.
keywords          : "keywords"
wordcount         : "TBC"
bibliography: "../resources/bib/My Library.bib"
csl: "../resources/bib/apa.csl"
figsintext        : true
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
toc               : false
lang              : "en-US"
documentclass     : "apa7"
output:
  papaja::apa6_pdf
header-includes:
- \raggedbottom
editor_options: 
  chunk_output_type: console
---


```{r S3setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE)
# knitr::opts_chunk$set(eval = TRUE, echo = TRUE)
#knitr::opts_chunk$set(include = FALSE)
```


```{r S3load_libraries_cogload}
rm(list = ls())
library(citr)
#install.packages("sjstats")
library(plyr)
library(foreign)
library(car)
library(desnum)
library(ggplot2)
library(extrafont)
#devtools::install_github("crsh/papaja")
library(papaja)
#library("dplyr")
library("afex")
library("tibble")
library(scales)
#install.packages("metap")
library(metap)
library(pwr)
library(lsr)
#install.packages("sjstats")
library(sjstats)
library(DescTools)
#inatall.packages("ggstatsplot")
#library(ggstatsplot)
library(VGAM)
library(nnet)
library(mlogit)
library(reshape2)
#install.packages("powerMediation")
library("powerMediation")
library("ggpubr")


# library(rstatix)


#source("load_all_data.R")

#devtools::install_github("benmarwick/wordcountaddin")
#library(wordcountaddin)
#wordcountaddin::text_stats("cogload_1to5_25Sept19.Rmd")
#setwd("manuscript_prep")
getwd()
```



```{r S3LoadData}
#source("~/Dropbox/College/research/Research_general/cog_load/moral_dumbfounding_and_cognitive_load/read_and_sort_raw_data.R")
#source("~/Dropbox/College/research/Research_general/cog_load/moral_dumbfounding_and_cognitive_load/load_study6_data.R")
rm(list = ls())

df3 <- read.csv("../data/study5_data_long.csv")
df1 <- read.csv("../data/study5_data_wide.csv")
x <- read.csv("../data/study5_data_long_clean.csv")

MPS <- x %>% 
  select(R1,R2,R3,R4)

alpha1 <- ltm::cronbach.alpha(MPS)

alpha1
```

# Study 3 - Good and Bad Characters
In Study 1 we found evidence for the moral dilution effect for judgments of *bad* moral characters. In Study 2 we failed replicate this effect for judgments of *good* moral characters. The aim of Study 3 was to test if valence (good vs. bad) moderates the moral dilution effect. We hypothesized that valence (good vs bad) would interact with condition in producing a dilution effect, such that the dilution effect would be observed for bad characters but not for good characters. Study 3 was pre-registered at \color{blue}[https://aspredicted.org/QDF_XT1](https://aspredicted.org/QDF_XT1)\color{black}.


## Study 3: Method
### Study 3: Participants and design
Study 3 was a 2 $\times$ 2 within-subjects factorial design. The first independent variable was condition with two levels, diagnostic and non-diagnostic. The second independent variable was valence of character description, with two levels morally good and morally bad. We used the same two dependent variables as in previous studies, the four item moral perception scale (MPS-4, $\alpha$ = `r round(alpha1$alpha,digits=2)`), and the single item moral perception measure MM-1.

A total sample of `r length(levels(as.factor(df3$ResponseId)))` (`r sum(df1$gender=="1",na.rm=T)` female, `r sum(df1$gender=="2", na.rm=T)` male, `r round(sum(df1$gender=="3", na.rm=T)/1)` non-binary, `r round(sum(df1$gender=="4", na.rm=T))` other; `r sum(df1$gender=="5", na.rm=T)` prefer not to say, *M*~age~ = `r round(mean(df3$age, na.rm=T),digits=2)`, min = `r min(df3$age, na.rm=T)`, max = `r max(df3$age, na.rm=T)`, *SD* = `r round(sd(df3$age, na.rm=T),digits=2)`) started the survey.  Participants were recruited from MTurk and paid $0.40 for their participation.

```{r}
df1 <- read.csv("../data/study5_data_long.csv")
df3 <- read.csv("../data/study5_data_long_clean.csv")
df_long_clean <- df3
table(df3$gender)
length(df1$gender)/6
length(levels(as.factor(df1$ResponseId)))-length(levels(as.factor(df3$ResponseId)))
length(df3$gender)/4

att_both <- length(levels(as.factor(df1$ResponseId)))-length(levels(as.factor(df3$ResponseId)))
```


```{r}
df_long_clean <- df3

x <- df3
x$attn_chk_1Q
x$attn_chk_2_Q
x <- x[which(x$attn_chk_2_Q==2|x$attn_chk_2_Q==5),]
x <- x[which(x$attn_chk_1Q==7),]
df_long_extra_clean <- x

x <- df3
# 
# df3 <- x
# att_both <- length(levels(as.factor(df1$ResponseId)))-length(levels(as.factor(df3$ResponseId)))


good <- x[which(x$valence=="good"),]
bad <- x[which(x$valence=="bad"),]

good$R_tot_recoded <- 7 - good$R_tot
bad$R_tot_recoded <- bad$R_tot

good$M1_recoded <- 100 - good$M1
bad$M1_recoded <- bad$M1

df_recoded <- rbind(good,bad)


x <- df_long_extra_clean

good <- x[which(x$valence=="good"),]
bad <- x[which(x$valence=="bad"),]

good$R_tot_recoded <- 7 - good$R_tot
bad$R_tot_recoded <- bad$R_tot

good$M1_recoded <- 100 - good$M1
bad$M1_recoded <- bad$M1

df_recoded_extra_clean <- rbind(good,bad)

x <- df_recoded_extra_clean
```

Participants who failed both manipulation checks were removed (*n* = `r att_both`), leaving a total sample of `r length(df3$gender)/4` participants (`r sum(df3$gender=="1",na.rm=T)/4` female, `r sum(df3$gender=="2", na.rm=T)/4` male, `r sum(df3$gender=="4", na.rm=T)/4` other, `r sum(df3$gender=="4", na.rm=T)/4` prefer not to say; *M*~age~ = `r round(mean(df3$age, na.rm=T),digits=2)`, min = `r min(df3$age, na.rm=T)`, max = `r max(df3$age, na.rm=T)`, *SD* = `r round(sd(df3$age, na.rm=T),digits=2)`).


### Study 3: Procedure and materials
Again, data were collected using an online questionnaire presented with Qualtrics (www.qualtrics.com). Participants were presented with four descriptions of characters taken from Studies 1 and 2. To ensure consistency across character judgments, we selected descriptions that related to the same moral foundations (care, fairness, and loyalty). We used the same four character names as in previous studies. The *good* characters were *Sam* and *Robin*, and the *bad* characters were *Francis* and *Alex*, e.g., *Imagine a person named Robin. Throughout their life they have been known to show compassion and empathy for others, act with a sense of fairness and justice, and, never to break their word.* or, *Imagine a person named Alex. Throughout their life they have been known to be cruel, act unfairly, and to betray their own group.* Full descriptions for each character are in the supplementary materials. One description for each the *good* and *bad* characters was randomly assigned to include non-diagnostic information for each participant thus all participants were exposed to all conditions (see \color{blue}[https://osf.io/mdnpv/?view_only=77883e3fbc3d45f1a35fe92d5318cb67](https://osf.io/mdnpv/?view_only=77883e3fbc3d45f1a35fe92d5318cb67)\color{black}  for details of the randomization blocks). Study 3 was pre-registered at \color{blue}[https://aspredicted.org/QDF_XT1](https://aspredicted.org/QDF_XT1)\color{black}


## Study 3: Results


```{r}
x <- df3
sam <- x[which(x$scenario=="sam"),]
francis <- x[which(x$scenario=="francis"),]
alex <- x[which(x$scenario=="alex"),]
robin <- x[which(x$scenario=="robin"),]

```

```{r}
x <- df3
tapply(x$R_tot, x$scenario, descriptives)
# bad <- x[which(x$condition=="diagnostic"),]
# good <- x[which(x$condition=="non-diagnostic"),]
#good$scenario_abb <- droplevels(good$scenario_abb)
x$valence
#x <- bad
aov_full <- rstatix::anova_test(
  data=x
  , dv=R_tot
  , wid = ResponseId
  , within = scenario)
aov1 <- rstatix::get_anova_table(aov_full)
aov1
aov1$DFd

pwc <- x %>%
  rstatix::pairwise_t_test(
    R_tot ~ scenario, paired = TRUE,
    p.adjust.method = "bonferroni"
    )
pwc
p_report(pwc$p[2])

# d1 <- lsr::cohensD(R_tot~condition,x,method="paired")
# t.test(R_tot~condition,x,paired=TRUE)
# t1 <- t.test(x$R_tot~x$scenario,paired=TRUE)
# d1
lapply(pwc$p.adj,p_report)
```




The means and standard deviations for MPS-4 for each scenario are as follows: 
*Sam* (good),
*M*~MPS-4~ = `r mean(sam$R_tot)`, *SD*~MPS-4~ = `r sd(sam$R_tot)`,
*Francis* (bad),
*M*~MPS-4~ = `r mean(francis$R_tot)`, *SD*~MPS-4~ = `r sd(francis$R_tot)`,
*Alex* (bad),
*M*~MPS-4~ = `r mean(alex$R_tot)`, *SD*~MPS-4~ = `r sd(alex$R_tot)`,
*Robin* (good),
*M*~MPS-4~ = `r mean(robin$R_tot)`, *SD*~MPS-4~ = `r sd(robin$R_tot)`. There was significant variation depending on the description, *F*(`r round(aov1$DFn)`,`r round(aov1$DFd)`) = `r aov1$F`, *p* `r paste(p_report(aov1$p))`, partial $\eta$^2^ = `r aov1$ges`. Both the *good* characters (*Robin* and *Sam*) were rated significantly more favorably than both the *bad* characters (*Alex* and *Francis*; all *p*s < .001). There were no differences between *Robin* and *Sam* (*good*: *p* `r paste(p_report(pwc$p[6]))`) or between *Alex* and *Francis* (*bad*; *p* `r paste(p_report(pwc$p[1]))`). 



```{r}
x <- df3
# bad <- x[which(x$condition=="diagnostic"),]
# good <- x[which(x$condition=="non-diagnostic"),]
#good$scenario_abb <- droplevels(good$scenario_abb)

#x <- bad
aov_full <- rstatix::anova_test(
  data=x
  , dv=M1
  , wid = ResponseId
  , within = scenario)
aov1 <- rstatix::get_anova_table(aov_full)
aov1
aov1$DFd

pwc <- x %>%
  rstatix::pairwise_t_test(
    M1 ~ scenario, paired = TRUE,
    p.adjust.method = "bonferroni"
    )
pwc
p_report(pwc$p[2])
lapply(pwc$p.adj, p_report)
paste(pwc$p.adj[2])
pwc$p[2]
# d1 <- lsr::cohensD(M1~condition,x,method="paired")
# t.test(M1~scenario,x,paired=TRUE)
# t1 <- t.test(x$M1~x$scenaro,paired=TRUE)
# d1

```

The means and standard deviations for MM-1 for each scenario are as follows: 
*Sam* (good),
*M*~MM-1~ = `r mean(sam$M1)`, *SD*~MM-1~ = `r sd(sam$M1)`;
*Francis* (bad),
*M*~MM-1~ = `r mean(francis$M1)`, *SD*~MM-1~ = `r sd(francis$M1)`;
*Alex* (bad),
*M*~MM-1~ = `r mean(alex$M1)`, *SD*~MM-1~ = `r sd(alex$M1)`;
*Robin* (good),
*M*~MM-1~ = `r mean(robin$M1)`, *SD*~MM-1~ = `r sd(robin$M1)`. There was significant variation depending on the description, *F*(`r round(aov1$DFn)`,`r round(aov1$DFd)`) = `r aov1$F`, *p* `r paste(p_report(aov1$p))`, partial $\eta$^2^ = `r paste(aov1$ges)`. Again, the *good* characters (*Robin* and *Sam*) were rated significantly more favorably than the *bad* characters (*Alex* and *Francis*; all *p*s < .001). There were no differences between *Robin* and *Sam* (*good*: *p* `r paste(p_report(pwc$p[6]))`) or between *Alex* and *Francis* (*bad*; *p* `r paste(p_report(pwc$p[1]))`). 



```{r}
x <- df3
x <- df_recoded

#x <- df_recoded_extra_clean


model0 <- lmerTest::lmer(R_tot_recoded ~ 1
                #   condition
                 + (1|ResponseId)
                # + (1|ResponseId:condition)
                , data = x
          #      , contrasts = list(condition = contr.sum  , valence = contr.sum)
            )

summary(model0)
model1 <- lmerTest::lmer(R_tot ~
                  condition*scenario
                + (1|ResponseId)
                + (1|ResponseId:condition)
                , data = x
                , contrasts = list(condition = contr.sum  )#, valence = contr.sum)
            )



model1 <- lmerTest::lmer(R_tot_recoded ~
                  condition*valence
                + (1|ResponseId)
                + (1|ResponseId:condition)
                + (1|ResponseId:valence)
                , data = x
                , contrasts = list(condition = contr.sum, valence = contr.sum )#, valence = contr.sum)
            )
summary(model1)
anova(model1)
results_anova <- as.data.frame(anova(model0,model1))
results_anova
results_anova$Chisq[2]
results_anova$Df
p1 <- results_anova$`Pr(>Chisq)`[2]
p_report(p1)
#p_report(results_anova$`Pr(>Chisq)`)[2]
results_anova$AIC
summary_model1 <- summary(model1)
summary_model1
results_coef <- as.data.frame(summary_model1$coefficients)
results_coef

aov1 <- anova(model1)
f3a <- aov1$`F value`[1]
f3b <- aov1$`F value`[2]
f3c <- aov1$`F value`[3]
p3a <- aov1$`Pr(>F)`[1]
p3b <- aov1$`Pr(>F)`[2]
p3c <- aov1$`Pr(>F)`[3]

results_coef$Estimate[2]
results_coef$`Std. Error`[2]
results_coef$df[2]
t1 <- results_coef$`t value`[2]
p2 <- results_coef$`Pr(>|t|)`[2]

#QuantPsyc::lm.beta(results_coef)
anova(model1)
```

We conducted a linear-mixed-effects model to test if our predictors influenced MPS-4 responses. Our outcome measure was MPS-4, our predictor variables were condition and valence; we allowed intercepts and the effects of condition and valence to vary across participants.
Overall, the model significantly predicted participants responses, and provided a better fit for the data than the baseline model,
$\chi$^2^(`r results_anova$Df[2]`) = `r results_anova$Chisq[2]`, *p* `r paste(p_report(p1))`. 
Overall, there was a significant main effect for condition,
*F*(`r aov1$NumDF[1]`, `r round(aov1$DenDF[1])`) = `r f3a`, *p* `r paste(p_report(p3a))`;
valence significantly predicted responses,
*F*(`r aov1$NumDF[2]`, `r round(aov1$DenDF[2])`) = `r f3b`, *p* `r paste(p_report(p3b))`;
and there was no significant condition $\times$ valence interaction,
*F*(`r aov1$NumDF[3]`, `r round(aov1$DenDF[3])`) = `r f3c`, *p* `r paste(p_report(p3c))`.



```{r}
x <- df3
x <- df_recoded
model0 <- lmerTest::lmer(M1 ~ 1
                #   condition
                 + (1|ResponseId)
                # + (1|ResponseId:condition)
                , data = x
          #      , contrasts = list(condition = contr.sum  , valence = contr.sum)
            )

summary(model0)
model1 <- lmerTest::lmer(M1 ~
                  condition*scenario
                + (1|ResponseId)
                + (1|ResponseId:condition)
                , data = x
                , contrasts = list(condition = contr.sum  )#, valence = contr.sum)
            )



model1 <- lmerTest::lmer(M1_recoded ~
                  condition*valence
                + (1|ResponseId)
                + (1|ResponseId:condition)
                + (1|ResponseId:valence)
                , data = x
                , contrasts = list(condition = contr.sum, valence = contr.sum )#, valence = contr.sum)
            )
summary(model1)
anova(model1)
results_anova <- as.data.frame(anova(model0,model1))
results_anova
results_anova$Chisq[2]
results_anova$Df
p1 <- results_anova$`Pr(>Chisq)`[2]
p_report(p1)
#p_report(results_anova$`Pr(>Chisq)`)[2]
results_anova$AIC
summary_model1 <- summary(model1)
summary_model1
results_coef <- as.data.frame(summary_model1$coefficients)
results_coef

aov1 <- anova(model1)
f3a <- aov1$`F value`[1]
f3b <- aov1$`F value`[2]
f3c <- aov1$`F value`[3]
p3a <- aov1$`Pr(>F)`[1]
p3b <- aov1$`Pr(>F)`[2]
p3c <- aov1$`Pr(>F)`[3]

results_coef$Estimate[2]
results_coef$`Std. Error`[2]
results_coef$df[2]
t1 <- results_coef$`t value`[2]
p2 <- results_coef$`Pr(>|t|)`[2]

#QuantPsyc::lm.beta(results_coef)
anova(model1)
```

We conducted a linear-mixed-effects model to test if our predictors influenced MM-1 responses. The model was the same as the previous model, with a change to the outcome measure, our outcome measure for this model was MM-1. As above, our predictor variables were condition and valence; we allowed intercepts and the effects of condition and valence to vary across participants.
Overall, the model significantly predicted participants responses, and provided a better fit for the data than the baseline model,
$\chi$^2^(`r results_anova$Df[2]`) = `r results_anova$Chisq[2]`, *p* `r paste(p_report(p1))`. 
Overall there was a main effect for condition,
*F*(`r aov1$NumDF[1]`, `r round(aov1$DenDF[1])`) = `r f3a`, *p* `r paste(p_report(p3a))`;
valence significantly predicted responses,
*F*(`r aov1$NumDF[2]`, `r round(aov1$DenDF[2])`) = `r f3b`, *p* `r paste(p_report(p3b))`;
and there was no significant condition $\times$ valence interaction,
*F*(`r aov1$NumDF[3]`, `r round(aov1$DenDF[3])`) = `r f3c`, *p* `r paste(p_report(p3c))`.

For both MP-4 and MM-1 we found a main effect for condition and valence, and there was no condition $\times$ valence interaction. We conducted follow-up analyses to test the if the main effect for condition holds for both good and bad descriptions separately.

## Differences in the *Bad* Descriptions





```{r}
x <- df3

#x <- df_long_extra_clean

x <- x[which(x$valence=="bad"),]


model0 <- lmerTest::lmer(R_tot ~ 1
                #   condition
                 + (1|ResponseId)
                # + (1|ResponseId:condition)
                , data = x
                #, contrasts = list(condition = contr.sum  , valence = contr.sum)
            )

summary(model0)
model1 <- lmerTest::lmer(R_tot ~
                  condition*scenario
                + (1|ResponseId)
             #   + (1|ResponseId:condition)
                , data = x
                , contrasts = list(condition = contr.sum  , scenario = contr.sum)
            )
anova(model1)
summary(model1)
results_anova <- as.data.frame(anova(model0,model1))
results_anova
results_anova$Chisq[2]
results_anova$Df
p1 <- results_anova$`Pr(>Chisq)`[2]
p_report(p1)
#p_report(results_anova$`Pr(>Chisq)`)[2]
results_anova$AIC
summary_model1 <- summary(model1)


results_coef <- as.data.frame(summary_model1$coefficients)

aov1 <- anova(model1)
f3 <- aov1$`F value`[1]
p3 <- aov1$`Pr(>F)`[1]


results_coef$Estimate[2]
results_coef$`Std. Error`[2]
results_coef$df[2]
results_coef$`t value`[2]
t1 <- results_coef$`t value`[2]

p2 <- results_coef$`Pr(>|t|)`[2]

#QuantPsyc::lm.beta(results_coef)
anova(model1)



```

We conducted a linear-mixed-effects model to test if condition influenced MPS-4 responses. Our outcome measure was MPS-4, our predictor variable was condition; we allowed intercepts and the effect of condition to vary across participants. Overall, the model did not significantly predict participants responses, or provide a better fit for the data than the baseline model, $\chi$^2^(`r results_anova$Df[2]`) = `r results_anova$Chisq[2]`, *p* `r paste(p_report(p1))`. Condition did not significantly influence MPS-4 responses *F*(`r aov1$NumDF[1]`, `r aov1$DenDF[1]`) = `r f3`, *p* `r paste(p_report(p3))`, and was not a significant predictor in the model $b$ = `r results_coef$Estimate[2]`, *t*(`r results_coef$df[2]`) = `r t1`, *p* `r paste(p_report(p2))`, see Figure\ \@ref(fig:S3bothconditionplot).





```{r}
x <- df3
df4 <- df_long_extra_clean
x <- df_long_extra_clean

x <- x[which(x$valence=="bad"),]


model0 <- lmerTest::lmer(R_tot ~ 1
                #   condition
                 + (1|ResponseId)
                # + (1|ResponseId:condition)
                , data = x
                #, contrasts = list(condition = contr.sum  , valence = contr.sum)
            )

summary(model0)
model1 <- lmerTest::lmer(R_tot ~
                  condition*scenario
                + (1|ResponseId)
             #   + (1|ResponseId:condition)
                , data = x
                , contrasts = list(condition = contr.sum  , scenario = contr.sum)
            )
anova(model1)
summary(model1)
results_anova <- as.data.frame(anova(model0,model1))
results_anova
results_anova$Chisq[2]
results_anova$Df
p1 <- results_anova$`Pr(>Chisq)`[2]
p_report(p1)
#p_report(results_anova$`Pr(>Chisq)`)[2]
results_anova$AIC
summary_model1 <- summary(model1)


results_coef <- as.data.frame(summary_model1$coefficients)

aov1 <- anova(model1)
f3 <- aov1$`F value`[1]
p3 <- aov1$`Pr(>F)`[1]


results_coef$Estimate[2]
results_coef$`Std. Error`[2]
results_coef$df[2]
results_coef$`t value`[2]
t1 <- results_coef$`t value`[2]

p2 <- results_coef$`Pr(>|t|)`[2]

#QuantPsyc::lm.beta(results_coef)
anova(model1)



```

There was a high degree of variability in the responses to the bad descriptions, with multiple participants rating the characters as good characters. It is possible that this reflects inattentive participants. Thus, as a follow-up exploratory analysis we employed a stricter measure of attention, and excluded participants who failed either attention check question. This left a sample of `r length(df4$gender)/4` participants (`r sum(df4$gender=="1",na.rm=T)/4` female, `r sum(df4$gender=="2", na.rm=T)/4` male, `r sum(df4$gender=="4", na.rm=T)/4` other, `r sum(df4$gender=="4", na.rm=T)/4` prefer not to say; *M*~age~ = `r round(mean(df4$age, na.rm=T),digits=2)`, min = `r min(df4$age, na.rm=T)`, max = `r max(df4$age, na.rm=T)`, *SD* = `r round(sd(df4$age, na.rm=T),digits=2)`). Using this stricter attention measure we conducted an additional linear-mixed-effects model to test if condition influenced MPS-4 responses. Overall, the model did not significantly predict participants responses, or provide a better fit for the data than the baseline model, $\chi$^2^(`r results_anova$Df[2]`) = `r results_anova$Chisq[2]`, *p* `r paste(p_report(p1))`. Condition did not significantly influence MPS-4 responses *F*(`r aov1$NumDF[1]`, `r aov1$DenDF[1]`) = `r f3`, *p* `r paste(p_report(p3))`, and was not a significant predictor in the model $b$ = `r results_coef$Estimate[2]`, *t*(`r results_coef$df[2]`) = `r t1`, *p* `r paste(p_report(p2))`.



```{r}
x <- df3

x <- x[which(x$valence=="bad"),]


model0 <- lmerTest::lmer(M1 ~ 1
                #   condition
                 + (1|ResponseId)
                # + (1|ResponseId:condition)
                , data = x
                #, contrasts = list(condition = contr.sum  , valence = contr.sum)
            )

summary(model0)
model1 <- lmerTest::lmer(M1 ~
                  condition*scenario
                + (1|ResponseId)
             #   + (1|ResponseId:condition)
                , data = x
                , contrasts = list(condition = contr.sum  , scenario = contr.sum)
            )
anova(model1)
summary(model1)
results_anova <- as.data.frame(anova(model0,model1))
results_anova
results_anova$Chisq[2]
results_anova$Df
p1 <- results_anova$`Pr(>Chisq)`[2]
p_report(p1)
#p_report(results_anova$`Pr(>Chisq)`)[2]
results_anova$AIC
summary_model1 <- summary(model1)


results_coef <- as.data.frame(summary_model1$coefficients)

aov1 <- anova(model1)
f3 <- aov1$`F value`[1]
p3 <- aov1$`Pr(>F)`[1]


results_coef$Estimate[2]
results_coef$`Std. Error`[2]
results_coef$df[2]
results_coef$`t value`[2]
t1 <- results_coef$`t value`[2]

p2 <- results_coef$`Pr(>|t|)`[2]

#QuantPsyc::lm.beta(results_coef)
anova(model1)



```

We conducted a linear-mixed-effects model to test if condition influenced MM-1 responses. Our outcome measure was MM-1, our predictor variable was condition; we allowed intercepts and the effect of condition to vary across participants. Overall, the model significantly predicted participants responses, and provided a better fit for the data than the baseline model, $\chi$^2^(`r results_anova$Df[2]`) = `r results_anova$Chisq[2]`, *p* `r paste(p_report(p1))`. Condition significantly influenced MM-1 responses *F*(`r aov1$NumDF[1]`, `r aov1$DenDF[1]`) = `r f3`, *p* `r paste(p_report(p3))`, and was a significant predictor in the model $b$ = `r results_coef$Estimate[2]`, *t*(`r results_coef$df[2]`) = `r t1`, *p* `r paste(p_report(p2))`, see Figure\ \@ref(fig:S3bothconditionplot).



## Differences in the *Good* Descriptions

To interpret the interaction effect, we conducted separate analyses for the Good and Bad descriptions.



```{r}
x <- df3

x <- x[which(x$valence=="good"),]


model0 <- lmerTest::lmer(R_tot ~ 1
                #   condition
                 + (1|ResponseId)
                # + (1|ResponseId:condition)
                , data = x
                #, contrasts = list(condition = contr.sum  , valence = contr.sum)
            )

summary(model0)
model1 <- lmerTest::lmer(R_tot ~
                  condition*scenario
                + (1|ResponseId)
             #   + (1|ResponseId:condition)
                , data = x
                , contrasts = list(condition = contr.sum  , scenario = contr.sum)
            )
anova(model1)
summary(model1)
results_anova <- as.data.frame(anova(model0,model1))
results_anova
results_anova$Chisq[2]
results_anova$Df
p1 <- results_anova$`Pr(>Chisq)`[2]
p_report(p1)
#p_report(results_anova$`Pr(>Chisq)`)[2]
results_anova$AIC
summary_model1 <- summary(model1)


results_coef <- as.data.frame(summary_model1$coefficients)

aov1 <- anova(model1)
f3 <- aov1$`F value`[1]
p3 <- aov1$`Pr(>F)`[1]


results_coef$Estimate[2]
results_coef$`Std. Error`[2]
results_coef$df[2]
results_coef$`t value`[2]
t1 <- results_coef$`t value`[2]

p2 <- results_coef$`Pr(>|t|)`[2]

#QuantPsyc::lm.beta(results_coef)
anova(model1)



```

We conducted a linear-mixed-effects model to test if condition influenced MPS-4 responses. Our outcome measure was MPS-4, our predictor variable was condition; we allowed intercepts and the effect of condition to vary across participants. Overall, the model significantly predicted participants responses, and provided a better fit for the data than the baseline model, $\chi$^2^(`r results_anova$Df[2]`) = `r results_anova$Chisq[2]`, *p* `r paste(p_report(p1))`. Condition significantly influenced MPS-4 responses *F*(`r aov1$NumDF[1]`, `r aov1$DenDF[1]`) = `r f3`, *p* `r paste(p_report(p3))`, and was a significant predictor in the model $b$ = `r results_coef$Estimate[2]`, *t*(`r results_coef$df[2]`) = `r t1`, *p* `r paste(p_report(p2))`, see Figure\ \@ref(fig:S3bothconditionplot).



```{r}
x <- df3

x$Valence <- dplyr::recode(x$valence
              , "good" = "Good"
              , "bad" = "Bad")

```


```{r S3Rtotconditionplot, fig.cap="Study 3: Differences in MPS-4 depending on condition", include=FALSE}

mps4plot <- 
ggplot(x,aes(x=condition,y=R_tot))+
  geom_violin() +
  stat_summary(fun=mean, geom="point", shape=23, size=2)+
  geom_boxplot(width=0.1)+
#  geom_dotplot(binaxis='y', stackdir='center', dotsize=.05)+
# violin plot with jittered points
# 0.2 : degree of jitter in x direction
  geom_jitter(shape=16
              , position=position_jitter(0.15)
              , size=.1
              , color="dark grey") +
  xlab("Condition") +
  ylab("MPS-4") +
  facet_grid(cols = vars(Valence)) +
  theme_bw() +
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
        panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
                                size=12
                                ),
        legend.text=element_text(#family="Times",
                                 size=8
                                 ),
          legend.title=element_text(#family="Times",
                                    size=10
                                    ),
          axis.text=element_text(#family="Times",
                                 colour = "black",
                                 size=8
                                 ),
          axis.ticks.x = element_blank(),
          axis.title=element_text(#family="Times",
                                  size=12
                                  ),
          strip.text=element_text(#family = "Times",
                                  size = 12
                                  ),
         # strip.background = element_rect(fill = "white"),
          legend.position="right")




```


```{r S3M1conditionplot, fig.cap="Study 3: Differences in MM1 depending on condition", include=FALSE, out.width = "50%"}

M1plot <- 
  ggplot(x,aes(x=condition,y=M1))+
  geom_violin() +
  stat_summary(fun=mean, geom="point", shape=23, size=2)+
  geom_boxplot(width=0.1)+
  #  geom_dotplot(binaxis='y', stackdir='center', dotsize=.05)+
  # violin plot with jittered points
  # 0.2 : degree of jitter in x direction
  geom_jitter(shape=16
              , position=position_jitter(0.15)
              , size=.1
              , color="dark grey") +
  xlab("Condition") +
  ylab("MM-1")+
  facet_grid(cols = vars(Valence)) +
  theme_bw() +
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
        panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
          size=12
        ),
        legend.text=element_text(#family="Times",
          size=8
        ),
        legend.title=element_text(#family="Times",
          size=10
        ),
        axis.text=element_text(#family="Times",
          colour = "black",
          size=8
        ),
        axis.ticks.x = element_blank(),
        axis.title=element_text(#family="Times",
          size=12
        ),
        strip.text=element_text(#family = "Times",
          size = 12
        ),
        # strip.background = element_rect(fill = "white"),
        legend.position="right")




```

```{r}
figure <- ggarrange(mps4plot
                    , M1plot
                    #,labels = c("A")
                    , ncol = 1
                    , nrow = 2
                    #, widths = c(0.485, 0.5)
                    )
figure
```


```{r S3bothconditionplot, fig.cap="Study 3: Differences in moral perception depending on condition", include=TRUE, fig.width = 5, fig.height = 7.5}

suppressWarnings(print(figure))

```



```{r}
x <- df3

x <- x[which(x$valence=="good"),]


model0 <- lmerTest::lmer(M1 ~ 1
                #   condition
                 + (1|ResponseId)
                # + (1|ResponseId:condition)
                , data = x
                #, contrasts = list(condition = contr.sum  , valence = contr.sum)
            )

summary(model0)
model1 <- lmerTest::lmer(M1 ~
                  condition#*scenario
                + (1|ResponseId)
             #   + (1|ResponseId:condition)
                , data = x
                , contrasts = list(condition = contr.sum  , scenario = contr.sum)
            )
anova(model1)
summary(model1)
results_anova <- as.data.frame(anova(model0,model1))
results_anova
results_anova$Chisq[2]
results_anova$Df
p1 <- results_anova$`Pr(>Chisq)`[2]
p_report(p1)
#p_report(results_anova$`Pr(>Chisq)`)[2]
results_anova$AIC
summary_model1 <- summary(model1)


results_coef <- as.data.frame(summary_model1$coefficients)

aov1 <- anova(model1)
f3 <- aov1$`F value`[1]
p3 <- aov1$`Pr(>F)`[1]


results_coef$Estimate[2]
results_coef$`Std. Error`[2]
round(results_coef$df[2])
results_coef$`t value`[2]
t1 <- results_coef$`t value`[2]

p2 <- results_coef$`Pr(>|t|)`[2]

#QuantPsyc::lm.beta(results_coef)
anova(model1)



```

We conducted a linear-mixed-effects model to test if condition influenced MM-1 responses. Our outcome measure was MM-1, our predictor variable was condition; we allowed intercepts and the effect of condition to vary across participants. Overall, the model significantly predicted participants responses, and provided a better fit for the data than the baseline model, $\chi$^2^(`r results_anova$Df[2]`) = `r results_anova$Chisq[2]`, *p* `r paste(p_report(p1))`. Condition significantly influenced MM-1 responses *F*(`r aov1$NumDF[1]`, `r round(aov1$DenDF[1])`) = `r f3`, *p* `r paste(p_report(p3))`, and was a significant predictor in the model $b$ = `r results_coef$Estimate[2]`, *t*(`r round(results_coef$df[2])`) = `r t1`, *p* `r paste(p_report(p2))`, see Figure\ \@ref(fig:S3bothconditionplot).

In the supplementary analyses we report the effect of condition on moral perception for each description individually.

The aim of Study 3 was to test if the moral dilution effect was moderated by valence of description. Based on the results of Studies 1 and 2 we hypothesized that a dilution effect would be observed for judgments of *bad* characters, but not for judgments of *good* characters. Interestingly, in Study 2 we found a dilution effect for *good* characters across both measures, however we only found a dilution effect for *bad* characters when using the single item measure of moral perception. 

