---
title: "Sample Analysis Pilot"
author: "Cillian McHugh"
date: "31st January 2022"
bibliography: "resources/bib/My Library.bib"
csl: "resources/bib/apa.csl"
output:
  bookdown::html_document2:
    fig_caption: yes
    toc: true
    toc_float:
      toc_collapsed: false
    toc_depth: 4
    number_sections: false
editor_options: 
  chunk_output_type: console
---

# Pilot Study

Below is the analysis for the pilot study.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
#knitr::opts_chunk$set(eval = TRUE, echo = TRUE)
knitr::opts_chunk$set(include = FALSE)
```

# Setting Up
## Load Libraries

```{r, results = "hide"}

rm(list = ls())
# devtools::install_github("cillianmiltown/R_desnum")
#install.packages("PowerTOST")
library(desnum)
library(psych)
library(corx)
library(nlme)
library(lme4)
library(TOSTER)
library(scales)
#install.packages("ez")
suppressMessages(library(tidyverse))
suppressMessages(library(car))
# library("PowerTOST")
```


## Run Script to set up Data
```{r, echo=TRUE}

source("pilot_set_up_data.R")
#source("pilot_simulating_data.R")
# create functions
#source("create_functions.R")

x <- full_long
x <- full_long_clean
length(x$gender)/6

sum(x$gender=="Female",na.rm = T)

```

# Overview
Below is an analysis of the pilot study, with a total sample of *N* = `r length(x$gender)/6`, (female = `r sum(x$gender=="Female",na.rm = T)/6`, male = `r sum(x$gender=="Male",na.rm = T)/6`, non-binary = `r sum(x$gender=="Non-binary / third gender",na.rm = T)/6`, prefer not to say = `r sum(x$gender=="Prefer not to say",na.rm = T)/6`, *M~age~* = `r round(mean(x$age,na.rm = T),digits=1)`, *SD* = `r round(sd(x$age,na.rm = T),digits=1)`).

## Measures

```{r}


MPS <- x %>% 
  select(MP_R1,MP_R2,MP_R3,MP_R4)

alpha1 <- ltm::cronbach.alpha(MPS)

x$MPS <- 
  x %>% 
  select(MP_R1,MP_R2,MP_R3,MP_R4) %>% 
  rowMeans()

rowMeans(MPS)

ltm::cronbach.alpha(MPS)

t_paragraph(x$M_1,x$condition,"moral perception")


t_paragraph(x$MPS,x$condition,"moral perception")


model1 <- lme4::lmer(M_1 ~ 
                  condition+scenario_abb
                + (1|ResponseId)
                , data = x
               # , family=gaussian
            )


summary(model1)

#lmer(M_1~condition+scenario_abb,data = x, random = ~ 1 | ResponseId)

mean(x$MP_R1)
t_paired_paragraph2 <- function (x, y, measure) 
{
    t <- t.test(x, y, paired = TRUE)
    d <- lsr::cohensD(x,y,method = "paired")
    d <- round(d,digits = 2)
    labels <- measure
    tsl <- as.vector(t$statistic)
    ts <- round(tsl, digits = 3)
    tpl <- as.vector(t$p.value)
    tp <- round(tpl, digits = 3)
    d_fl <- as.vector(t$parameter)
    d_f <- round(d_fl, digits = 2)
    mxl <- as.vector(mean(x))
    mx <- round(mxl, digits = 2)
    myl <- as.vector(mean(y))
    my <- round(myl, digits = 2)
    sdxl <- as.vector(sd(x))
    sdx <- round(sdxl, digits = 2)
    sdyl <- as.vector(sd(y))
    sdy <- round(sdyl, digits = 2)
    if (tp < 0.05) 
        print(paste0("A paired samples t-test revealed a significant difference in ", 
            measure, " between the Diagnostic Condition, (M = ", mx, ", SD = ", 
            sdx, "), and the Non-Diagnostic condition, (M =", my, ", SD = ", sdy, 
            "), t(", d_f, ") = ", ts, ", p = ", tp, ", d = ", d, "."), quote = FALSE)
    if (tp > 0.05) 
        print(paste0("A paired samples t-test revealed no difference in ", 
            measure, " between the Diagnostic Condition, (M = ", mx, ", SD = ", 
            sdx, "), and the Non-Diagnostic Condition, (M =", my, ", SD = ", sdy, 
            "), t(", d_f, ") = ", ts, ", p = ", tp, ", d = ", d, "."), quote = FALSE)
}

```

We used two measures of moral perception. The first measure Moral Perception Scale (MPS) four items rated on 7-point Likert scales (with anchors Bad/Good, Immoral/Moral, Violent/Peaceful, Merciless/Empathetic), this showed excellent reliability &alpha; = `r round(alpha1$alpha,digits=2)`, *M* = `r round(mean(x$MPS),digits=1)`, *SD* = `r round(sd(x$MPS),digits=1)`. The second measure was a single item Moral Perception Measure (M1), participants were asked to "Please Rate [character name] according to immoral or moral you view them" on a slider rating from 0-100 with (0 = *Very Immoral*, and 100 = *Very Moral*); *M* = `r round(mean(x$M_1),digits=1)`, *SD* = `r round(sd(x$M_1),digits=1)`.

## Differences in M1

```{r}
M1 <- x %>% 
  select("ResponseId","condition","scenario_abb","M_1") %>% 
  pivot_wider(names_from = scenario_abb, values_from = M_1)

M1$M1 <- NA

D <- M1[which(M1$condition=="Diagnostic"),]
ND <- M1[which(M1$condition=="Non-Diagnostic"),]

#D$M1 <- 
D$M1 <- D %>% select("Sam","Francis","Alex","Robin") %>% rowMeans()
ND$M1 <- ND %>% select("Charlie","Jackie") %>% rowMeans()

M2 <- rbind(D,ND)
M3 <- M2 %>% 
  select("ResponseId","condition","M1") %>% 
  pivot_wider(names_from = condition, values_from = M1)

M4 <- 
M3 %>% pivot_longer(
  cols = c("Diagnostic","Non-Diagnostic"),
  names_to = "condition",
  values_to = "M1"
)

t <- t.test(M3$Diagnostic,M3$`Non-Diagnostic`,paired = T)

```

```{r include=TRUE}
t_paired_paragraph2(M3$Diagnostic,M3$`Non-Diagnostic`, "moral Perception")
```


```{r, include=TRUE}

ggplot(M4,aes(x=condition,y=M1))+
  geom_violin() +
  stat_summary(fun=mean, geom="point", shape=23, size=2)+
  geom_boxplot(width=0.1)+
#  geom_dotplot(binaxis='y', stackdir='center', dotsize=.05)+
# violin plot with jittered points
# 0.2 : degree of jitter in x direction
  geom_jitter(shape=16, position=position_jitter(0.15), size=.8, color="dark grey")
# violin plot with median points
#p + stat_summary(fun.y=median, geom="point", size=.2, color="red")

```


```{r include=TRUE}
ez::ezANOVA(data=x,dv=.(M_1),wid=.(ResponseId),within=.(scenario_abb),type=3)
```

```{r include=TRUE}

ggplot(x,aes(x=scenario_abb,y=M_1))+
  geom_violin() +
  stat_summary(fun=mean, geom="point", shape=23, size=.5)+
  geom_boxplot(width=0.1)+
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=.5)+
# violin plot with jittered points
# 0.2 : degree of jitter in x direction
  geom_jitter(shape=16, position=position_jitter(0.15), size = .3, color="dark grey")
# violin plot with median points
#p + stat_summary(fun.y=median, geom="point", size=.2, color="red")

```



## Differences in MPS


```{r}
M1 <- x %>% 
  select("ResponseId","condition","scenario_abb","MPS") %>% 
  pivot_wider(names_from = scenario_abb, values_from = MPS)

M1$M1 <- NA

D <- M1[which(M1$condition=="Diagnostic"),]
ND <- M1[which(M1$condition=="Non-Diagnostic"),]

#D$M1 <- 
D$M1 <- D %>% select("Sam","Francis","Alex","Robin") %>% rowMeans()
ND$M1 <- ND %>% select("Charlie","Jackie") %>% rowMeans()

M2 <- rbind(D,ND)
M3 <- M2 %>% 
  select("ResponseId","condition","M1") %>% 
  pivot_wider(names_from = condition, values_from = M1)

M4 <- 
M3 %>% pivot_longer(
  cols = c("Diagnostic","Non-Diagnostic"),
  names_to = "condition",
  values_to = "M1"
)

t <- t.test(M3$Diagnostic,M3$`Non-Diagnostic`,paired = T)
lsr::cohensD(M3$Diagnostic,M3$`Non-Diagnostic`,method = "paired")


```

```{r include=TRUE}
t_paired_paragraph2(M3$Diagnostic,M3$`Non-Diagnostic`, "moral Perception")
```

```{r include=TRUE}

ggplot(M4,aes(x=condition,y=M1))+
  geom_violin() +
  stat_summary(fun=mean, geom="point", shape=23, size=1)+
  geom_boxplot(width=0.1)+
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=.5)+
# violin plot with jittered points
# 0.2 : degree of jitter in x direction
  geom_jitter(shape=16, position=position_jitter(0.15), size = .8, color="dark grey")
# violin plot with median points
#p + stat_summary(fun.y=median, geom="point", size=.2, color="red")

```


```{r include=TRUE}
ez::ezANOVA(data=x,dv=.(MPS),wid=.(ResponseId),within=.(scenario_abb),type=3)
```

```{r, include=TRUE}

ggplot(x,aes(x=scenario_abb,y=MPS))+
  geom_violin() +
  stat_summary(fun=mean, geom="point", shape=23, size=2)+
  geom_boxplot(width=0.1)+
#  geom_dotplot(binaxis='y', stackdir='center', dotsize=.05)+
# violin plot with jittered points
# 0.2 : degree of jitter in x direction
  geom_jitter(shape=16, position=position_jitter(0.15), size=.3, color="dark grey")
# violin plot with median points
#p + stat_summary(fun.y=median, geom="point", size=.2, color="red")

```


```{r, include = FALSE, echo = FALSE}
# 
# #y <- table(df3$InCS,df3$condition)
# y <- table(x$action_choice,x$scenario)
# y <- as.data.frame(y)
# #colnames(y) <- c("condition","InCS","Freq")
# colnames(y) <- c("action_choice","scenario","Freq")
# 
# z <- as.data.frame(table(x$action_choice,x$scenario)/length(x$gender)*2)
# 
# 
# 
# z <- rbind(as.data.frame(table(x$action_choice[which(x$scenario=="wave")])/
#                            length(x$action_choice[which(x$scenario=="wave")])),
#            as.data.frame(table(x$action_choice[which(x$scenario=="beckon")])/
#                            length(x$action_choice[which(x$scenario=="beckon")])))
# 
# 
# perc <- z$Freq
# test <- cbind(y,perc)
```

```{r, include = FALSE, echo = FALSE}
# 
# ggplot(test, aes(x=scenario, y=perc, fill=factor(action_choice,labels=c("Act","Do not Act")
#                                                       ))) +
#   scale_y_continuous(limits = c(-.03,1),
#                      labels = percent_format()
#   )+ 
#   geom_col(position = "dodge",
#            color="black",
#            size=.2
#   )+
#   geom_text(family = "Times", size=4.2,
#             aes( label = scales::percent(test$perc),
#                  y= perc ),
#             stat= "identity",
#             vjust = -.5,
#             position = position_dodge(.9),
#             fontface='plain'
#             )+
#   geom_text(family = "Times", size=4.2,
#             aes(label = format(Freq),
#                 y= -3*(..count../100)/(..count..)),
#             stat= "count",
#             position = position_dodge(0.9),
#             #vjust = -.05,
#             fontface='plain'
#             ) +
#   xlab("Scenario") +
#   ylab("Percentage of participants selecting each response")+
#   scale_x_discrete(labels=c("Beckon", "Wave")) +
#   scale_fill_grey(start = .5, end = .8) +
#   labs(fill="Action Choice") +
#   
#   geom_text(family = "Times", size=4.2,
#             aes( label = scales::percent(test$perc),
#                  y= test$perc ),
#             stat= "identity",
#             vjust = -.5,
#             position = position_dodge(.9),
#             fontface='plain'
#             )+
#   #theme_apa() +
#   theme_bw() +
#   theme(plot.title=element_text(family="Times",
#                                 size=12
#                                 ),
#         legend.text=element_text(family="Times",
#                                  size=8
#                                  ),
#           legend.title=element_text(family="Times",
#                                     size=10
#                                     ),
#           axis.text=element_text(family="Times",
#                                  colour = "black",
#                                  size=10
#                                  ),
#           axis.ticks.x = element_blank(),
#           axis.title=element_text(family="Times",
#                                   size=12
#                                   ),
#           strip.text=element_text(family = "Times",
#                                   size = 12
#                                   ),
#           strip.background = element_rect(fill = "white"),
#           legend.position="right")

```

