---
title: "Sample Analysis Study 2"
author: "Cillian McHugh"
date: "5th April 2022"
bibliography: "resources/bib/My Library.bib"
csl: "resources/bib/apa.csl"
output:
  bookdown::html_document2:
    fig_caption: yes
    toc: true
    toc_float:
      toc_collapsed: false
    toc_depth: 4
    number_sections: false
editor_options: 
  chunk_output_type: console
---

# Study 2

Below is the analysis for positive moral dilution study.

```{r setup, include=FALSE}
# Setting Up

knitr::opts_chunk$set(echo = FALSE)
#knitr::opts_chunk$set(eval = TRUE, echo = TRUE)
knitr::opts_chunk$set(include = FALSE)
```


```{r, results = "hide"}
## Load Libraries

rm(list = ls())
# devtools::install_github("cillianmiltown/R_desnum")
#install.packages("PowerTOST")
library(desnum)
library(psych)
library(corx)
library(nlme)
library(lme4)
library(TOSTER)
library(scales)
library(ez)

#install.packages("ez")
suppressMessages(library(tidyverse))
suppressMessages(library(car))
# library("PowerTOST")
```


```{r, echo=TRUE}
## Run Script to set up Data

source("study4_set_up_data.R")
# 
# write.csv(df_wide_clean, file = "data/study_1_wide_clean.csv")
# write.csv(df_long_clean, file = "data/study_1_long_clean.csv")

#source("pilot_simulating_data.R")
# create functions
#source("create_functions.R")

x <- df_long
x <- df_long_clean


sum(x$gender=="1",na.rm = T)/4

```

```{r include=TRUE}
## Measures


MPS <- x %>% 
  select(R1,R2,R3,R4)

alpha1 <- ltm::cronbach.alpha(MPS)

alpha1

```

```{r}
length(x$gender)/4
sum(x$gender=="1")/4
sum(x$gender=="2")/4
sum(x$gender=="3")/4
sum(x$gender=="4")/4
sum(x$gender=="5")/4

# 1 = male
# 2 = female
# 3 = non-binary
# 4 = prefer to self describe
# 5 = prefer not to say

round(mean(x$age),digits=1)

```
# Overview
## Sample
Below is a sample analysis for a moral dilution study, with a total sample of *N* = `r length(x$gender)/4`, (female = `r sum(x$gender=="2")/4`, male = `r sum(x$gender=="1")/4`, non-binary/other = `r sum(x$gender=="3")/4 + sum(x$gender=="5")/4`, prefer not to say `r sum(x$gender=="5")/4`, *M~age~* = `r round(mean(x$age),digits=1)`, *SD* = `r round(sd(x$age),digits=1)`).
```{r}
x <- df_long_clean
x <- x[which(x$Sample=="student"),]
```
### Student Sample
The majority of participants were from the student body: *n* = `r length(x$gender)/4`, (female = `r sum(x$gender=="2")/4`, male = `r sum(x$gender=="1")/4`, non-binary/other = `r sum(x$gender=="3")/4 + sum(x$gender=="5")/4`, prefer not to say `r sum(x$gender=="5")/4`, *M~age~* = `r round(mean(x$age),digits=1)`, *SD* = `r round(sd(x$age),digits=1)`).

```{r}
x <- df_long_clean
x <- x[which(x$Sample=="MTurk"),]
```
### MTurk
In order to reach our pre-registered target sample size we recruited additional participants from MTurk: *n* = `r length(x$gender)/4`, (female = `r sum(x$gender=="2")/4`, male = `r sum(x$gender=="1")/4`, non-binary/other = `r sum(x$gender=="3")/4 + sum(x$gender=="5")/4`, prefer not to say `r sum(x$gender=="5")/4`, *M~age~* = `r round(mean(x$age),digits=1)`, *SD* = `r round(sd(x$age),digits=1)`).

```{r}
x <- df_long_clean
```

## Differences in M1

```{r include=TRUE}

model1 <- lme4::lmer(M1 ~
                  condition+scenario
                + (1|ResponseId)
                , data = x
               # , family=gaussian
            )
summary(model1)
anova(model1)


library(nlme)

m0 <- nlme::lme(M1 ~ 
                  1
                , random=~1|ResponseId
                , data=x
                , method = "ML")
m1 <- nlme::lme(M1 ~ 
                  condition*scenario
                , random=~1|ResponseId
                , data=x
                , method = "ML")
summary(m1)


anova(m0,m1)
anova(m1)

```


```{r, include=TRUE}
ezANOVA(data = x, dv = .(M1), wid = .(ResponseId),
        within = .(condition), detailed = FALSE, type = 2)
```



```{r}
# library(rstatix)
# x$ResponseId_factor <- as.factor(x$ResponseId)
# res.aov <- anova_test(
#   data = x, dv = M1, wid = ResponseId,
#   within = c(condition)
#   )
# get_anova_table(res.aov)
# 
# test.aov <- with(x,
#                    aov(M1 ~ condition + scenario + (condition * scenario) +
#                        Error(ResponseId / (condition * scenario)))
# )
# 
# summary(test.aov)
# 
# library(ez)
# ezANOVA(data = x, dv = .(M1), wid = .(ResponseId),
#         within = .(scenario), detailed = FALSE, type = 2)
# 
# 
# model1 <- lme(M1 ~ condition*scenario, random = ~1|ResponseId, data = x, method = "ML")
# 
# baseline <- lme(M1 ~ 1, random = ~1|ResponseId, data = x, method = "ML")
# 
# #postHocs<- multcomp::glht(model1, linfct = multcomp::mcp(c(condition*scenario) = "Tukey"))
# #summary(postHocs)
# 
# anova(baseline,model1)
# 
# summary(model1)

```


### Main Effect for Condition

```{r, include=TRUE}

ggplot(x,aes(x=condition,y=M1))+
  geom_violin() +
  stat_summary(fun=mean, geom="point", shape=23, size=2)+
  geom_boxplot(width=0.1)+
#  geom_dotplot(binaxis='y', stackdir='center', dotsize=.05)+
# violin plot with jittered points
# 0.2 : degree of jitter in x direction
  geom_jitter(shape=16, position=position_jitter(0.15), size=.3, color="dark grey")
# violin plot with median points
#p + stat_summary(fun.y=median, geom="point", size=.2, color="red")

```

### Main Effect for Scenario

```{r include=TRUE}

ggplot(x,aes(x=scenario,y=M1))+
  geom_violin() +
  stat_summary(fun=mean, geom="point", shape=23, size=.5)+
  geom_boxplot(width=0.1)+
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=.5)+
# violin plot with jittered points
# 0.2 : degree of jitter in x direction
  geom_jitter(shape=16, position=position_jitter(0.15), size = .3, color="dark grey")
# violin plot with median points
#p + stat_summary(fun.y=median, geom="point", size=.2, color="red")

```




## Differences in four item Measure

```{r include=TRUE}

# model1 <- lme4::lmer(R_tot ~ 
#                   condition+scenario
#                 + (1|ResponseId)
#                 , data = x
#                # , family=gaussian
#             )
# anova(model1)


library(nlme)
m1 <- nlme::lme(R_tot ~ 
                  condition*scenario
                , random=~1|ResponseId
                , data=x)
summary(m1)

anova(m1)

```


```{r, include=TRUE}
ezANOVA(data = x, dv = .(R_tot), wid = .(ResponseId),
        within = .(condition), detailed = FALSE, type = 2)
```


### Main Effect for Condition

```{r, include=TRUE}

ggplot(x,aes(x=condition,y=R_tot))+
  geom_violin() +
  stat_summary(fun=mean, geom="point", shape=23, size=2)+
  geom_boxplot(width=0.1)+
#  geom_dotplot(binaxis='y', stackdir='center', dotsize=.05)+
# violin plot with jittered points
# 0.2 : degree of jitter in x direction
  geom_jitter(shape=16, position=position_jitter(0.15), size=.3, color="dark grey")
# violin plot with median points
#p + stat_summary(fun.y=median, geom="point", size=.2, color="red")

```

### Main Effect for Scenario

```{r include=TRUE}

ggplot(x,aes(x=scenario,y=R_tot))+
  geom_violin() +
  stat_summary(fun=mean, geom="point", shape=23, size=.5)+
  geom_boxplot(width=0.1)+
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=.5)+
# violin plot with jittered points
# 0.2 : degree of jitter in x direction
  geom_jitter(shape=16, position=position_jitter(0.15), size = .3, color="dark grey")
# violin plot with median points
#p + stat_summary(fun.y=median, geom="point", size=.2, color="red")

```


