---
title: "Sample Analysis Study 3"
author: "Cillian McHugh"
date: "12th April 2022"
bibliography: "resources/bib/My Library.bib"
csl: "resources/bib/apa.csl"
output:
  bookdown::html_document2:
    fig_caption: yes
    toc: true
    toc_float:
      toc_collapsed: false
    toc_depth: 4
    number_sections: false
editor_options: 
  chunk_output_type: console
---

# Study 3

Below is the analysis for positive moral dilution study.

```{r setup, include=FALSE}
# Setting Up

knitr::opts_chunk$set(echo = FALSE)
#knitr::opts_chunk$set(eval = TRUE, echo = TRUE)
knitr::opts_chunk$set(include = FALSE)
```


```{r, results = "hide"}
## Load Libraries

rm(list = ls())
# devtools::install_github("cillianmiltown/R_desnum")
#install.packages("PowerTOST")
library(desnum)
library(psych)
library(corx)
library(nlme)
library(lme4)
library(TOSTER)
library(scales)
library(ez)

#install.packages("ez")
suppressMessages(library(tidyverse))
suppressMessages(library(car))
# library("PowerTOST")
```


```{r, echo=TRUE}
## Run Script to set up Data

source("study5_set_up_data.R")
# 
# write.csv(df_wide_clean, file = "data/study_1_wide_clean.csv")
# write.csv(df_long_clean, file = "data/study_1_long_clean.csv")

#source("pilot_simulating_data.R")
# create functions
#source("create_functions.R")

x <- df_long
x <- df_long_clean


sum(x$gender=="1",na.rm = T)/4

```

```{r include=TRUE}
## Measures


MPS <- x %>% 
  select(R1,R2,R3,R4)

alpha1 <- ltm::cronbach.alpha(MPS)

alpha1

```

```{r}
length(x$gender)/4
sum(x$gender=="1")/4
sum(x$gender=="2")/4
sum(x$gender=="3")/4
sum(x$gender=="4")/4
sum(x$gender=="5")/4

# 1 = male
# 2 = female
# 3 = non-binary
# 4 = prefer to self describe
# 5 = prefer not to say

round(mean(x$age),digits=1)

```
# Overview
## Sample
Below is a sample analysis for a moral dilution study, with a total sample of *N* = `r length(x$gender)/4`, (female = `r sum(x$gender=="2")/4`, male = `r sum(x$gender=="1")/4`, non-binary/other = `r sum(x$gender=="3")/4 + sum(x$gender=="5")/4`, prefer not to say `r sum(x$gender=="5")/4`, *M~age~* = `r round(mean(x$age),digits=1)`, *SD* = `r round(sd(x$age),digits=1)`).

```{r}
x <- df_long_clean
```

## Testing for Interaction Effect



## Four item Measure

```{r include=FALSE}

# model1 <- lme4::lmer(R_tot ~ 
#                   condition+scenario
#                 + (1|ResponseId)
#                 , data = x
#                # , family=gaussian
#             )
# anova(model1)


library(nlme)
m1 <- nlme::lme(R_tot ~ 
                  condition*valence
                , random=~1|ResponseId
                , data=x)
summary(m1)

anova(m1)

```


```{r, include=TRUE}
ezANOVA(data = x, dv = .(R_tot), wid = .(ResponseId),
        within = .(condition,valence), detailed = FALSE, type = 2)
```


### Condition vs Valence

```{r, include=TRUE}

ggplot(x,aes(x=condition,y=R_tot))+
  geom_violin() +
  stat_summary(fun=mean, geom="point", shape=23, size=2)+
  geom_boxplot(width=0.1)+
#  geom_dotplot(binaxis='y', stackdir='center', dotsize=.05)+
# violin plot with jittered points
# 0.2 : degree of jitter in x direction
  geom_jitter(shape=16, position=position_jitter(0.15), size=.3, color="dark grey")+
  facet_grid(cols = vars(valence))
# violin plot with median points
#p + stat_summary(fun.y=median, geom="point", size=.2, color="red")

```

### Differences between Scenarios

```{r include=TRUE}

ggplot(x,aes(x=scenario,y=R_tot))+
  geom_violin() +
  stat_summary(fun=mean, geom="point", shape=23, size=.5)+
  geom_boxplot(width=0.1)+
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=.5)+
# violin plot with jittered points
# 0.2 : degree of jitter in x direction
  geom_jitter(shape=16, position=position_jitter(0.15), size = .3, color="dark grey")
# violin plot with median points
#p + stat_summary(fun.y=median, geom="point", size=.2, color="red")

```



### Single Item Measure

```{r include=FALSE}

model1 <- lme4::lmer(M1 ~
                  condition+scenario
                + (1|ResponseId)
                , data = x
               # , family=gaussian
            )
summary(model1)
anova(model1)


library(nlme)

m0 <- nlme::lme(M1 ~ 
                  1
                , random=~1|ResponseId
                , data=x
                , method = "ML")
m1 <- nlme::lme(M1 ~ 
                  condition*valence
                , random=~1|ResponseId
                , data=x
                , method = "ML")
summary(m1)


anova(m0,m1)
anova(m1)

```


```{r, include=TRUE}
ezANOVA(data = x, dv = .(M1), wid = .(ResponseId),
        within = .(condition,valence), detailed = FALSE, type = 2)
```


```{r}
# library(rstatix)
# x$ResponseId_factor <- as.factor(x$ResponseId)
# res.aov <- anova_test(
#   data = x, dv = M1, wid = ResponseId,
#   within = c(condition)
#   )
# get_anova_table(res.aov)
# 
# test.aov <- with(x,
#                    aov(M1 ~ condition + scenario + (condition * scenario) +
#                        Error(ResponseId / (condition * scenario)))
# )
# 
# summary(test.aov)
# # 
# ezANOVA(data = x, dv = .(M1), wid = .(ResponseId),
#         within = .(condition,valence), detailed = FALSE, type = 2)

# 
# model1 <- lme(M1 ~ condition*scenario, random = ~1|ResponseId, data = x, method = "ML")
# 
# baseline <- lme(M1 ~ 1, random = ~1|ResponseId, data = x, method = "ML")
# 
# #postHocs<- multcomp::glht(model1, linfct = multcomp::mcp(c(condition*scenario) = "Tukey"))
# #summary(postHocs)
# 
# anova(baseline,model1)
# 
# summary(model1)

```


### Condition vs Valence

```{r, include=TRUE}

ggplot(x,aes(x=factor(condition),y=M1))+
  geom_violin() +
  stat_summary(fun=mean, geom="point", shape=23, size=2)+
  geom_boxplot(width=0.1)+
#  geom_dotplot(binaxis='y', stackdir='center', dotsize=.05)+
# violin plot with jittered points
# 0.2 : degree of jitter in x direction
  geom_jitter(shape=16, position=position_jitter(0.15), size=.3, color="dark grey")+
  facet_grid(cols = vars(valence))
# violin plot with median points
#p + stat_summary(fun.y=median, geom="point", size=.2, color="red")

```

### Differences between Scenarios

```{r include=TRUE}

ggplot(x,aes(x=scenario,y=M1))+
  geom_violin() +
  stat_summary(fun=mean, geom="point", shape=23, size=.5)+
  geom_boxplot(width=0.1)+
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=.5)+
# violin plot with jittered points
# 0.2 : degree of jitter in x direction
  geom_jitter(shape=16, position=position_jitter(0.15), size = .3, color="dark grey")
# violin plot with median points
#p + stat_summary(fun.y=median, geom="point", size=.2, color="red")

```



## Testing Good and Bad Separately

### Bad

#### Four Item Measure

```{r, include=TRUE}

df <- df_long_clean


x <- df[which(df$valence=="bad"),]

tapply(x$R_tot, x$condition, descriptives)

m1 <- nlme::lme(R_tot ~ 
                  condition
                , random=~1|ResponseId
                , data=x)
summary(m1)

anova(m1)

ezANOVA(data = x, dv = .(R_tot), wid = .(ResponseId),
        within = .(condition), detailed = FALSE, type = 2)

```

#### Single Item Measure

```{r, include=TRUE}

df <- df_long_clean


x <- df[which(df$valence=="bad"),]

tapply(x$M1, x$condition, descriptives)

m1 <- nlme::lme(M1 ~ 
                  condition
                , random=~1|ResponseId
                , data=x)
summary(m1)

anova(m1)

ezANOVA(data = x, dv = .(M1), wid = .(ResponseId),
        within = .(condition), detailed = FALSE, type = 2)

```

### Good

#### Four Item Measure

```{r, include=TRUE}

df <- df_long_clean


x <- df[which(df$valence=="good"),]


tapply(x$R_tot, x$condition, descriptives)

m1 <- nlme::lme(R_tot ~ 
                  condition
                , random=~1|ResponseId
                , data=x)
summary(m1)

anova(m1)

ezANOVA(data = x, dv = .(R_tot), wid = .(ResponseId),
        within = .(condition), detailed = FALSE, type = 2)

```

#### Single Item Measure

```{r, include=TRUE}

df <- df_long_clean


x <- df[which(df$valence=="good"),]


tapply(x$M1, x$condition, descriptives)

m1 <- nlme::lme(M1 ~ 
                  condition
                , random=~1|ResponseId
                , data=x)
summary(m1)

anova(m1)

ezANOVA(data = x, dv = .(M1), wid = .(ResponseId),
        within = .(condition), detailed = FALSE, type = 2)

```

## Recoded Test
The above analyses showed an interaction between valence and condition showing an effect for condition in both "good" and "bad" scenarios, and this effect was in opposite directions (as would be expected based on the measures used). Below we have recoded a new variable "strength of judgement" to test if the strength of the effect of condition is different depending on valence.

```{r}

df <- df_long_clean

df$R_tot_strength <- rep(NA)
df$M1_strength <- rep(NA)

good <- df[which(df$valence=="good"),]

bad <- df[which(df$valence=="bad"),]

good$R_tot_strength <- good$R_tot
good$M1_strength <- good$M1


bad$R_tot_strength <- 7 - bad$R_tot
bad$M1_strength <- 100 - bad$M1

x <- rbind(good,bad)

```



## Testing for Interaction Effect



## Four item Measure


```{r, include=TRUE}
ezANOVA(data = x, dv = .(R_tot_strength), wid = .(ResponseId),
        within = .(condition,valence), detailed = FALSE, type = 2)
```




### Single Item Measure


```{r, include=TRUE}
ezANOVA(data = x, dv = .(M1_strength), wid = .(ResponseId),
        within = .(condition,valence), detailed = FALSE, type = 2)
```
