---
title             : "Pilot Study 1"
shorttitle        : "Moral Dilution"
author:
  - name          : "Blinded"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Blinded"
    email         : "Blinded"
  - name          : "Blinded"
    affiliation   : "2"
  - name          : "Blinded"
    affiliation   : "1"
  - name          : "Blinded"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "Blinded"
  - id            : "2"
    institution   : "Blinded"
author_note: >
  All procedures performed in studies involving human participants were approved by institutional research ethics committee and conducted in accordance with the Code of Professional Ethics of the Psychological Society of Ireland, and with the 1964 Helsinki declaration and its later amendments or comparable ethical standards. Informed consent was obtained from all individual participants included in the study. The authors declare that there are no potential conflicts of interest with respect to the research, authorship, and/or publication of this article. All authors consented to the submission of this manuscript.
abstract: >
  Six studies etc.
keywords          : "keywords"
wordcount         : "TBC"
bibliography: "../resources/bib/My Library.bib"
csl: "../resources/bib/apa6.csl"
figsintext        : no
floatsintext      : no
figurelist        : yes
tablelist         : yes
footnotelist      : no
lineno            : no
toc               : false
lang              : "en-US"
documentclass     : "apa7"
output:
  papaja::apa6_word
header-includes:
- \raggedbottom
editor_options: 
  chunk_output_type: console
---



```{r pilot2setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE)
# knitr::opts_chunk$set(eval = TRUE, echo = TRUE)
#knitr::opts_chunk$set(include = FALSE)
```



```{r pilot2load_libraries_cogload}
rm(list = ls())
library(citr)
#install.packages("sjstats")
library(plyr)
library(foreign)
library(car)
library(desnum)
library(ggplot2)
library(extrafont)
#devtools::install_github("crsh/papaja")
library(papaja)
#library("dplyr")
library("afex")
library("tibble")
library(scales)
#install.packages("metap")
library(metap)
library(pwr)
library(lsr)
#install.packages("sjstats")
library(sjstats)
library(DescTools)
#inatall.packages("ggstatsplot")
#library(ggstatsplot)
library(VGAM)
library(nnet)
library(mlogit)
library(reshape2)
#install.packages("powerMediation")
library("powerMediation")
library("ggpubr")


#source("load_all_data.R")

#devtools::install_github("benmarwick/wordcountaddin")
#library(wordcountaddin)
#wordcountaddin::text_stats("cogload_1to5_25Sept19.Rmd")
#setwd("..")
#setwd("manuscript_prep")
getwd()
```


```{r pilot2LoadData}
#source("~/Dropbox/College/research/Research_general/cog_load/moral_dumbfounding_and_cognitive_load/read_and_sort_raw_data.R")
#source("~/Dropbox/College/research/Research_general/cog_load/moral_dumbfounding_and_cognitive_load/load_study6_data.R")
rm(list = ls())

df3 <- read.csv("../data/pilot_2_data_long.csv")

x <- read.csv("../data/pilot_2_data_long_clean.csv")

MPS <- x %>% 
  select(MP_R1,MP_R2,MP_R3,MP_R4)

alpha1 <- ltm::cronbach.alpha(MPS)

```

# Pilot Study 2
Study 1 showed the moral dilution effect for judgments of *bad* characters. The aim of this pilot study was to develop and test materials that may be used to study the moral dilution effect for judgments of morally *good* characters. As with Pilot Study 1, we developed diagnostic and non-diagnostic descriptions. We hypothesized that evaluations of the diagnostic descriptions would be more extreme (more moral) than for the non-diagnostic descriptions

## Pilot Study 2: Method
### Pilot 2: Participants and design
The pilot study was a within-subjects design. The independent variable was description type with two levels, *diagnostic* and *non-diagnostic*. We used the same two dependent variables as in previous studies, the four item moral perception scale (MPS-4,  $\alpha$ = `r round(alpha1$alpha,digits=2)`), and the single item moral perception measure (MM-1).

A total sample of `r length(df3$gender)/6` (`r sum(df3$gender=="Female",na.rm=T)/6` female, `r sum(df3$gender=="Male", na.rm=T)/6` male, `r sum(df3$gender=="Non-binary / third gender", na.rm=T)/6` non-binary, `r sum(df3$gender=="Prefer not to say", na.rm=T)/6` prefer not to say; *M*~age~ = `r round(mean(df3$age, na.rm=T),digits=2)`, min = `r min(df3$age, na.rm=T)`, max = `r max(df3$age, na.rm=T)`, *SD* = `r round(sd(df3$age, na.rm=T),digits=2)`) started the survey.  Participants were recruited from MTurk.

```{r}
df1 <- read.csv("../data/pilot_2_data_long.csv")
df3 <- read.csv("../data/pilot_2_data_long_clean.csv")
table(df3$gender)
att_both <- (length(df1$gender)/6)-(length(df3$gender)/6)
```


We removed participants who failed both manipulation checks (*n* = `r att_both`), leaving a total sample of `r length(df3$gender)/6` participants (`r sum(df3$gender=="Female",na.rm=T)/6` female, `r sum(df3$gender=="Male", na.rm=T)/6` male, `r sum(df3$gender=="Non-binary / third gender", na.rm=T)/6` non-binary, `r sum(df3$gender=="Prefer not to say", na.rm=T)/6` prefer not to say; *M*~age~ = `r round(mean(df3$age, na.rm=T),digits=2)`, min = `r min(df3$age, na.rm=T)`, max = `r max(df3$age, na.rm=T)`, *SD* = `r round(sd(df3$age, na.rm=T),digits=2)`).

### Pilot 2: Procedure and materials
Data were collected using an online questionnaire presented with Qualtrics (www.qualtrics.com).  Participants were presented with descriptions of six characters.

Moral character descriptions were developed by combining descriptions relating to three different moral foundations, focusing on upholding the moral foundations (rather than transgressions as in previous studies). A sample description reads: *Imagine a person named Sam. Throughout their life they have been known to always help and care for others, treat everyone fairly and equally, and show a strong sense of loyalty to others.*. Full text of these descriptions can be found in the supplementary materials. 

We developed neutral descriptions that included information relating to physical appearance/attributes, hobbies/activities, and a color preference, e.g., *Imagine a person named Charlie. They have blue eyes, drink coffee in the morning, and their favourite colour is green*.

We used the same gender ambiguous names, and we did not specify the gender of the characters. Pilot Study 2 was pre-registered at \color{blue}[https://aspredicted.org/W52_VPX](https://aspredicted.org/W52_VPX)\color{black}.

## Pilot 2: Results

```{r}
x <- df3
sam <- x[which(x$scenario_abb=="Sam"),]
francis <- x[which(x$scenario_abb=="Francis"),]
alex <- x[which(x$scenario_abb=="Alex"),]
robin <- x[which(x$scenario_abb=="Robin"),]
jackie <- x[which(x$scenario_abb=="Jackie"),]
charlie <- x[which(x$scenario_abb=="Charlie"),]

```

```{r}
x <- df3
bad <- x[which(x$condition=="Diagnostic"),]
good <- x[which(x$condition=="Non-Diagnostic"),]
#good$scenario_abb <- droplevels(good$scenario_abb)

x <- bad
aov_full <- rstatix::anova_test(
  data=x
  , dv=R_tot
  , wid = ResponseId
  , within = scenario_abb)
aov1 <- rstatix::get_anova_table(aov_full)
aov1
aov1$DFd

pwc <- x %>%
  rstatix::pairwise_t_test(
    R_tot ~ scenario_abb, paired = TRUE,
    p.adjust.method = "bonferroni"
    )
pwc


d1 <- lsr::cohensD(R_tot~scenario_abb,good,method="paired")
t.test(R_tot~scenario_abb,good,paired=TRUE)
t1 <- t.test(good$R_tot~good$scenario_abb,paired=TRUE)
d1

```


The means and standard deviations for MPS-4 for each scenario are as follows: 
*Sam* (diagnostic),
*M*~MPS-4~ = `r mean(sam$R_tot)`, *SD*~MPS-4~ = `r sd(sam$R_tot)`,
*Francis* (diagnostic),
*M*~MPS-4~ = `r mean(francis$R_tot)`, *SD*~MPS-4~ = `r sd(francis$R_tot)`,
*Alex* (diagnostic),
*M*~MPS-4~ = `r mean(alex$R_tot)`, *SD*~MPS-4~ = `r sd(alex$R_tot)`,
*Robin* (diagnostic),
*M*~MPS-4~ = `r mean(robin$R_tot)`, *SD*~MPS-4~ = `r sd(robin$R_tot)`,
*Jackie* (non-diagnostic),
*M*~MPS-4~ = `r mean(jackie$R_tot)`, *SD*~MPS-4~ = `r sd(jackie$R_tot)`,
*Charlie* (non-diagnostic),
*M*~MPS-4~ = `r mean(charlie$R_tot)`, *SD*~MPS-4~ = `r sd(charlie$R_tot)`. For the diagnostic descriptions, there was significant variation depending on the description, *F*(`r round(aov1$DFn)`,`r round(aov1$DFd)`) = `r aov1$F`, *p* `r paste(p_report(aov1$p))`, partial $\eta$^2^ = `r aov1$ges`, *Sam* was viewed significantly more favorably than *Francis* (*p* `r paste(p_report(pwc$p.adj[5]))`). For the non-diagnostic descriptions there was no significant difference in ratings depending on description, *t*(`r t1$parameter`) = `r t1$statistic`, *p* `r paste(p_report(t1$p.value))`, *d* = `r d1`.


```{r}
x <- df3
bad <- x[which(x$condition=="Diagnostic"),]
good <- x[which(x$condition=="Non-Diagnostic"),]
#good$scenario_abb <- droplevels(good$scenario_abb)

x <- bad
aov_full <- rstatix::anova_test(
  data=x
  , dv=M1
  , wid = ResponseId
  , within = scenario_abb)
aov1 <- rstatix::get_anova_table(aov_full)
aov1
aov1$DFd

pwc <- x %>%
  rstatix::pairwise_t_test(
    M1 ~ scenario_abb, paired = TRUE,
    p.adjust.method = "bonferroni"
    )
pwc


d1 <- lsr::cohensD(M1~scenario_abb,good,method="paired")
t.test(M1~scenario_abb,good,paired=TRUE)
t1 <- t.test(good$M1~good$scenario_abb,paired=TRUE)
d1

```

The means and standard deviations for MM-1 for each scenario are as follows: 
*Sam* (diagnostic),
*M*~MM-1~ = `r mean(sam$M1)`, *SD*~MM-1~ = `r sd(sam$M1)`;
*Francis* (diagnostic),
*M*~MM-1~ = `r mean(francis$M1)`, *SD*~MM-1~ = `r sd(francis$M1)`;
*Alex* (diagnostic),
*M*~MM-1~ = `r mean(alex$M1)`, *SD*~MM-1~ = `r sd(alex$M1)`;
*Robin* (diagnostic),
*M*~MM-1~ = `r mean(robin$M1)`, *SD*~MM-1~ = `r sd(robin$M1)`;
*Jackie* (non-diagnostic),
*M*~MM-1~ = `r mean(jackie$M1)`, *SD*~MM-1~ = `r sd(jackie$M1)`;
*Charlie* (non-diagnostic),
*M*~MM-1~ = `r mean(charlie$M1)`, *SD*~MM-1~ = `r sd(charlie$M1)`. For the diagnostic descriptions, we observed no significant variation depending on the description, *F*(`r round(aov1$DFn)`,`r round(aov1$DFd)`) = `r aov1$F`, *p* `r paste(p_report(aov1$p))`, partial $\eta$^2^ = `r paste(aov1$ges)`. For the non-diagnostic descriptions there was no significant difference in ratings depending on description, *t*(`r t1$parameter`) = `r t1$statistic`, *p* `r paste(p_report(t1$p.value))`, *d* = `r d1`.

```{r}
x <- df3
model0 <- lmerTest::lmer(R_tot ~ 1
                #   condition
                 + (1|ResponseId)
                # + (1|ResponseId:condition)
                , data = x
          #      , contrasts = list(condition = contr.sum  , valence = contr.sum)
            )

summary(model0)
model1 <- lmerTest::lmer(R_tot ~
                  condition
                + (1|ResponseId)
                + (1|ResponseId:condition)
                , data = x
                , contrasts = list(condition = contr.sum  )#, valence = contr.sum)
            )

results_anova <- as.data.frame(anova(model0,model1))
results_anova
results_anova$Chisq[2]
results_anova$Df
p1 <- results_anova$`Pr(>Chisq)`[2]
p_report(p1)
#p_report(results_anova$`Pr(>Chisq)`)[2]
results_anova$AIC
summary_model1 <- summary(model1)


results_coef <- as.data.frame(summary_model1$coefficients)

results_coef$Estimate[2]
results_coef$`Std. Error`[2]
results_coef$df[2]
t1 <- results_coef$`t value`[2]
p2 <- results_coef$`Pr(>|t|)`[2]

#QuantPsyc::lm.beta(results_coef)
anova(model1)
```

We conducted a linear-mixed-effects model to test if condition influenced MPS-4 responses. Our outcome measure was MPS-4, our predictor variable was condition; we allowed intercepts and the effect of condition to vary across participants.
Overall, the model significantly predicted participants responses, and provided a better fit for the data than the baseline model, $\chi$^2^(`r results_anova$Df[2]`) = `r results_anova$Chisq[2]`, *p* `r paste(p_report(p1))`. Condition was a significant predictor in the model $b$ = `r results_coef$Estimate[2]`, *t*(`r results_coef$df[2]`) = `r t1`, *p* `r paste(p_report(p2))`, with the diagnostic descriptions being rated as more moral than the non-diagnostic descriptions of immoral characters Figure\ \@ref(fig:pilot2bothconditionplot).

```{r pilot2Rtotconditionplot, fig.cap="Pilot Study 1: Differences in MPS-4 depending on condition", include=FALSE}

mps4plot <- ggplot(x,aes(x=condition,y=R_tot))+
  geom_violin() +
  stat_summary(fun=mean, geom="point", shape=23, size=2)+
  geom_boxplot(width=0.1)+
#  geom_dotplot(binaxis='y', stackdir='center', dotsize=.05)+
# violin plot with jittered points
# 0.2 : degree of jitter in x direction
  geom_jitter(shape=16
              , position=position_jitter(0.15)
              , size=.3
              , color="dark grey") +
  xlab("Condition") +
  ylab("Moral Perception Scale (MPS-4)") +
  theme_bw() +
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
        panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
                                size=12
                                ),
        legend.text=element_text(#family="Times",
                                 size=8
                                 ),
          legend.title=element_text(#family="Times",
                                    size=10
                                    ),
          axis.text=element_text(#family="Times",
                                 colour = "black",
                                 size=8
                                 ),
          axis.ticks.x = element_blank(),
          axis.title=element_text(#family="Times",
                                  size=12
                                  ),
          strip.text=element_text(#family = "Times",
                                  size = 12
                                  ),
         # strip.background = element_rect(fill = "white"),
          legend.position="right")




```


```{r pilot2M1conditionplot, fig.cap="Pilot Study 1: Differences in MM1 depending on condition", include=FALSE}

M1plot <- ggplot(x,aes(x=condition,y=M1))+
  geom_violin() +
  stat_summary(fun=mean, geom="point", shape=23, size=2)+
  geom_boxplot(width=0.1)+
#  geom_dotplot(binaxis='y', stackdir='center', dotsize=.05)+
# violin plot with jittered points
# 0.2 : degree of jitter in x direction
  geom_jitter(shape=16
              , position=position_jitter(0.15)
              , size=.3
              , color="dark grey") +
  xlab("Condition") +
  ylab("Moral Perception Measure (MM-1)")+
  theme_bw() +
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
        panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
                                size=12
                                ),
        legend.text=element_text(#family="Times",
                                 size=8
                                 ),
          legend.title=element_text(#family="Times",
                                    size=10
                                    ),
          axis.text=element_text(#family="Times",
                                 colour = "black",
                                 size=8
                                 ),
          axis.ticks.x = element_blank(),
          axis.title=element_text(#family="Times",
                                  size=12
                                  ),
          strip.text=element_text(#family = "Times",
                                  size = 12
                                  ),
         # strip.background = element_rect(fill = "white"),
          legend.position="right")




```


```{r}
figure <- ggarrange(mps4plot
                    , M1plot
                    #,labels = c("A")
                    , ncol = 2
                    , nrow = 1
                    , widths = c(0.485, 0.5))
figure
```


```{r pilot2bothconditionplot, fig.cap="Pilot Study 2: Differences in moral perception depending on condition", include=TRUE}

suppressWarnings(print(figure))

```



```{r}
model0 <- lmerTest::lmer(M1 ~ 1
                #   condition
                 + (1|ResponseId)
                # + (1|ResponseId:condition)
                , data = x
            #    , contrasts = list(condition = contr.sum  , valence = contr.sum)
            )

summary(model0)
model1 <- lmerTest::lmer(M1 ~
                  condition
                + (1|ResponseId)
                + (1|ResponseId:condition)
                , data = x
                , contrasts = list(condition = contr.sum  )#, valence = contr.sum)
            )

results_anova <- as.data.frame(anova(model0,model1))
results_anova
results_anova$Chisq[2]
results_anova$Df
p1 <- results_anova$`Pr(>Chisq)`[2]
p_report(p1)
#p_report(results_anova$`Pr(>Chisq)`)[2]
results_anova$AIC
summary_model1 <- summary(model1)


results_coef <- as.data.frame(summary_model1$coefficients)

results_coef$Estimate[2]
results_coef$`Std. Error`[2]
results_coef$df[2]
results_coef$`t value`[2]
t1 <- results_coef$`t value`[2]

p2 <- results_coef$`Pr(>|t|)`[2]

#QuantPsyc::lm.beta(results_coef)
anova(model1)
```


We conducted a linear-mixed-effects model to test if condition influenced MM-1 responses. Our outcome measure was MM-1, our predictor variable was condition; we allowed intercepts and the effect of condition to vary across participants. Overall, the model significantly predicted participants responses, and provided a better fit for the data than the baseline model, $\chi$^2^(`r results_anova$Df[2]`) = `r results_anova$Chisq[2]`, *p* `r paste(p_report(p1))`. Condition was a significant predictor in the model $b$ = `r results_coef$Estimate[2]`, *t*(`r results_coef$df[2]`) = `r t1`, *p* `r paste(p_report(p2))`, with the diagnostic descriptions being rated as more moral than the non-diagnostic descriptions, see Figure\ \@ref(fig:pilot2bothconditionplot).


